Appendix: A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-04 appendix.Rmd
update caption for sensitivity analysis

\begin{equation}
\label{eq:effect-size}
KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R}\sigma^2)|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\boldsymbol{\mu}_z\right).
\end{equation}

@@

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\\text{-value} = 0.05$. The area coloured in red indicates $\\text{adjusted }p\\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multiplier smaller than $1$, the adjusted $p$-value will incrase then decrase as $p$-value increases. The trend is the opposite for multiplier greater than $1$, but the difference will eventually reach $0$."}

>>>>

\begin{equation*}
\label{eq:effect-size}
KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R}\sigma^2)|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\boldsymbol{\mu}_z\right).
\end{equation*}

@@

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\\text{-value} = 0.05$. The area coloured in red indicates $\\text{adjusted }p\\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multipliers smaller than 1, the adjusted $p\\text{-value}$ will initially increase and decline when the $p\\text{-value}$ increases. The trend is opposite with multipliers greater than $1$, but the difference eventually reaches $0$."}

### 2023-04-04 appendix.tex
update caption for sensitivity analysis

\caption{Change of $p$-values with $\hat{\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\text{-value} = 0.05$. The area coloured in red indicates $\text{adjusted }p\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multiplier smaller than $1$, the adjusted $p$-value will incrase then decrase as $p$-value increases. The trend is the opposite for multiplier greater than $1$, but the difference will eventually reach $0$.}\label{fig:sensitivity}
\end{figure}

>>>>

\caption{Change of $p$-values with $\hat{\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\text{-value} = 0.05$. The area coloured in red indicates $\text{adjusted }p\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multipliers smaller than 1, the adjusted $p\text{-value}$ will initially increase and decline when the $p\text{-value}$ increases. The trend is opposite with multipliers greater than $1$, but the difference eventually reaches $0$.}\label{fig:sensitivity}
\end{figure}
